---
title: "Bev and other medications"
author: "Mustafa Ascha"
date: "December 4, 2018"
output:
  word_document: default
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(pander)
library(survminer)
library(gridExtra)
devtools::load_all("mabsr")
#if (!exists("results")) results   <-       read_rds("results/models-mabs.rds")
#if (!exists("ps"))      backup_ps <- ps <- read_rds("results/plots.rds")
backup_ps <- ps <- results$plots
#results[["to"]] <- read_rds("table-ones.rds")

hr_table <-
  plot_coxs(results, F) %>%
    filter(grepl("evacizumab", term) & !grepl(":", term)) %>%
    distinct() %>%
    modify_at("weighted", ~ gsub("not ", "un", .x)) %>%
    modify_at("phr", ~ ifelse(.x %in% c(0, 1e-4), " <0.001", .x)) %>%
    mutate(estimate = paste(hr, " (", lci, "-", hci, " p:", phr, ")", sep = "")) %>%
    filter(
      (weighted == "weighted" & pop == "Overall") | (pop == "Overall" & mdl == "mv") |
        (pop == "Brain Mets" & weighted != "weighted") |
        mdl == "st"
    ) %>%
    select(matched, pop, mdl, estimate) %>%
    #mutate(r = row_number()) %>%
    spread(pop, estimate) %>%
    arrange(desc(matched))

bm_mv_cox <- 
  results[["bm_mv_cox"]][[2]] %>% 
    mutate(HR = paste(estimate, " (", conf.low, "-", conf.high, ", p:", p.value, ")", sep = "")) %>% 
    select(term, Multivariable = HR) %>% 
    modify_at("term", ~ gsub("bmab01", "Bevacizumab", .x))

bm_uni_cox <- 
  results[["bm_propensity_hrs"]] %>% 
  map_dfr(2) %>% 
  distinct() %>% 
  filter(
    (weighted != "weighted")
    ) %>% 
  spread(matched, HR) %>% 
  select(-weighted) 

mv_cox <- 
  results[["mv_cox"]][[2]] %>% 
    mutate(HR = paste(estimate, " (", conf.low, "-", conf.high, ", p:", p.value, ")", sep = "")) %>% 
    select(term, Multivariable = HR) %>% 
    modify_at("term", ~ gsub("bmab01", "Bevacizumab", .x))

uni_cox <- 
  results[["propensity_hrs"]] %>% 
  map_dfr(2) %>% 
  distinct() %>% 
  filter(
    (weighted != "weighted" | (term == "Bevacizumab" & weighted == "weighted")) & 
      !(term == "Bevacizumab" & weighted == "not weighted")
    ) %>% 
  spread(matched, HR) %>% 
  select(-weighted) %>%
  filter(!grepl(":", term))

get_bev_hr <- function(mv_cox, uni_cox) {
  m <- 
    mv_cox %>% 
      filter(grepl("evacizu", term)) %>% 
      mutate(matched = "unmatched") %>% 
      select(term, matched, HR = Multivariable) %>% 
      mutate(mdl = "mv")
  u <- 
    uni_cox %>% 
      gather(matched, HR, -term) %>% 
      filter(grepl("evacizu", term)) %>% 
      mutate(mdl = "uni")
  bind_rows(m, u) %>% select(-term)
}

r_table <- 
map2_dfr(list(list(mv_cox, uni_cox), list(bm_mv_cox, bm_uni_cox)), 
     c("Overall", "Brain Mets"), 
     ~ get_bev_hr(.x[[1]], .x[[2]]) %>% mutate(pop = .y)) %>% 
  spread(pop, HR)

```

\pagebreak

# Figures

## Survival 

### Brain mets

```{r, fig.height=4.5, fig.width=6}

names(hr_table) <- gsub(" ", "_", names(hr_table))

ps$uni_cox_bm$plot  <-
  ps$uni_cox_bm$plot + 
  labs(color = "Treatment", fill = "Treatment", x = "")  + 
  annotate(
    geom = "label", 
    #label = paste("Brain Metastases Population\nUnivariable HR:\n", hr_table[["Overall"]][1]), 
    label = paste("Univariable HR:\n", with(hr_table, Brain_Mets[matched == "unmatched" & mdl == "uni"])), 
    #label = "Univariable", 
    x = 43.5, 
    y = 0.8
    )

ps$mv_cox_bm <- 
  ps$mv_cox_bm + 
  labs(color = "Treatment", x = "Time")  + 
  annotate(
    geom = "label", 
    #label = paste("Brain Metastases Population\nMultivariable HR:\n", hr_table[["Overall"]][1]), 
    label = paste("Multivariable HR:\n", with(hr_table, Brain_Mets[matched == "unmatched" & mdl == "mv"])), 
    #label = "Multivariable", 
    x = 43, 
    y = 0.8
    )  

```

```{r fig.height=6.5}
png("figs/bm-srv-bev.png", units = "in", width = 4, height = 6, res = 300)
arrange_srv(ps$uni_cox_bm$plot, ps$mv_cox_bm, ps$uni_cox_bm$table)
dev.off()
arrange_srv(ps$uni_cox_bm$plot, ps$mv_cox_bm, ps$uni_cox_bm$table)
```

\pagebreak

### Overall

```{r, fig.height=4.5, fig.width=6}
ps$uni_cox_ov$plot <- 
  ps$uni_cox_ov$plot + 
  labs(color = "Treatment", fill = "Treatment", x = "")  + 
  annotate(
    geom = "label", 
    label = paste("Univariable AHR:\n", with(hr_table, Overall[matched == "unmatched" & mdl == "uni"])), 
    x = 43.5, 
    y = 0.8
    )

ps$mv_cox_ov <- 
  ps$mv_cox_ov + 
  labs(color = "Treatment", fill = "Treatment", x = "Time")  + 
  annotate(
    geom = "label", 
    label = paste("Multivariable HR:\n", with(hr_table, Overall[matched == "unmatched" & mdl == "mv"])), 
    x = 43, 
    y = 0.8
    )
```

```{r fig.height=6.5}
png("figs/ov-srv-bev.png", units = "in", width = 4, height = 6, res = 300)
arrange_srv(ps$uni_cox_ov$plot, ps$mv_cox_ov, ps$uni_cox_ov$table)
dev.off()
arrange_srv(ps$uni_cox_ov$plot, ps$mv_cox_ov, ps$uni_cox_ov$table)
```

\pagebreak

# Tables

## Clinical and demographics table

```{r}
colnames(results$to[["br_bev"]]) <- gsub(":", "\n", colnames(results$to[["br_bev"]]))
results$to[["br_bev"]][,c(2, 1, 4, 3)] %>% pander(split.table = Inf)

cdt <- results$to[["br_bev"]][,c(2, 1, 4, 3)]
nms <- rownames(cdt)
rownames(cdt)  <- NULL
write_csv(data.frame(nms, cdt), "to.csv")
```

## Bevacizumab hazard ratios

```{r}
pander(hr_table)
```

\pagebreak

# Supplementary Material

## Figures

### Odds of Bevacizumab Treatment

```{r }
png("figs/odds-bev.png", units = "in", width = 4, height = 6, res = 300)
compose(glm_ggplot, plot_glms)(results) 
dev.off()
compose(glm_ggplot, plot_glms)(results) 
```

## Tables

### Hazards of mortality among patients with brain metastases

```{r}
bm_cox <- full_join(bm_mv_cox, bm_uni_cox) %>% select(term, Univariable = unmatched, Multivariable)
pander(bm_cox, split.table = Inf)
#write_csv(bm_cox, "cox-bm.csv")
```

### Hazards of mortality in the overall population

```{r}
overall_cox <- full_join(mv_cox, uni_cox) %>% select(term, Univariable = unmatched, Multivariable)
pander(overall_cox, split.table = Inf)
#write_csv(overall_cox, "cox-overall.csv")
```

### Odds of bevacizumab prescription: Brain Mets

```{r }
results[c("bm_uni_glm", "bm_mv_glm")] %>% 
  imap_dfr(function(dta, nm) {
    nm <- gsub("bm_", "", nm)
     dta %>% 
       modify_at(
         c("estimate", "conf.low", "conf.high"), 
         ~ sprintf("%.2f", as.numeric(.x))
       ) %>% 
       mutate(
         model = ifelse(nm == "mv_glm", "Multivariable", "Univariable"),
         OR = paste(estimate, " (", conf.low, "-", conf.high, ", p: ", p.value, ")", sep = "")
       )
   }) %>% 
    select(-estimate, -conf.low, -conf.high, -p.value) %>% 
    fix_term_names() %>% 
  spread(model, OR)  %>% 
  select(term, Univariable, Multivariable) %>%
  pander(split.table = Inf)
```

### Odds of bevacizumab prescription: Overall

```{r }
library(magrittr)
table_bev_odds(results[c("uni_glm", "mv_glm")])  %>% 
  select(term, Univariable, Multivariable) %>% 
  #write_csv("glm-o.csv") %T>% 
  pander(split.table = Inf)
```


### Exclusion and selection

```{r eval=FALSE}
ex <- read_rds("results/exclusion.rds")
#pander(ex, split.table = Inf)

nl <- select(mutate(ex$not_nscl, hc = as.character(Var2)), freq = Freq, hc)

sh <- 
  readxl::read_excel("documentation/seer_histo.xls") %>% 
  rename_all(~ gsub("[^A-Za-z]", "_", tolower(.x))) %>% 
  modify_at("histology_behavior", ~ gsub("\\/.*", "", .x)) %>% 
  select(hc = histology_behavior, hd = histology_description) %>% 
  distinct() %>% 
  left_join(nl) %>% 
  filter(!is.na(freq)) %>% 
  group_by(hd) %>% 
  summarise(
    cds = paste(unique(hc), collapse = ", "), 
    cnt = prettyNum(sum(freq), ",")
    ) 
  # pmap_chr(
  #   function(hd, cds, cnt) {
  #     p <- paste
  #     p(str_to_title(hd), " (", p(cds, collapse = ", "), ") - ", cnt, sep = "")
  # }) 

pander(sh)

r_these <- 
    c(
    "hmocnt"
    , "age_dx"
    , "typefup"
    , "med_stcd"
    , "race"
    , "srv_time_mon"
    , "vrfydth"
    , "payerdx_v"
  )

r_w <- 
  c(
    ""
    , "Age"
    , "Follow Up"
    , "Medicare"
    , "Race"
    , "Survival"
    , "Death verified"
    , "Insurance"
  ) 

exs <- 
  ex$exclusions %>% 
  (function(a) {
    data.frame(
      vrs = a$Vars, 
      vls = gsub("9999", "Unknown" ,a$Values), 
      n = as.numeric(unlist(a[1:14])), 
      stringsAsFactors = FALSE
      )
    }) %>%
  modify_at(
    "vrs",
    ~ reduce2(r_these, r_w, function(a, b, d) gsub(b, d, a), .init = .x)
    ) %>% 
  pmap_chr(function(vrs, vls, n) {
    paste(vrs, vls, "-", prettyNum(n, ","))
    }) %>% 
  trimws() %>%
  as.data.frame()
pander(exs)

```

### Propensity score distributions

```{r}
library(gridExtra)
library(zeallot)

ps_p <- function(ps) {
  p1 <- ps$unmatched
  p2 <- ps$matched
  list(
    p1 + 
      labs(x = "", y = "Count", fill = "") + 
      theme(
        legend.position = c(0.8, 0.7), 
        legend.background = element_blank(), 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        ) + 
      scale_fill_manual(labels = c("BEV-", "BEV+"), values = c("grey10", "grey60"))
    , 
    p2 + 
      labs(y = "Count", fill = "") + 
      theme(
        legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        ) + 
      scale_fill_manual(values = c("grey10", "grey60"))
  )
}

c(p1, p2) %<-% ps_p(results$overall_ps_plots)
grid.arrange(p1, p2, top = text_grob("Overall Population"))
png("figs/ov-ps.png", units = "in", width = 4, height = 6, res = 300)
grid.arrange(p1, p2, top = text_grob("Overall Population"))
dev.off()
```

```{r}
c(bm_p1, bm_p2) %<-% ps_p(results$bm_ps_plots)
png("figs/bm-ps.png", units = "in", width = 4, height = 6, res = 300)
grid.arrange(bm_p1, bm_p2, top = text_grob("SBM Population"))
dev.off()
grid.arrange(bm_p1, bm_p2, top = text_grob("SBM Population"))
```

```{r}
c(p1, p2) %<-% ps_p(results$overall_ps_plots)
c(bm_p1, bm_p2) %<-% ps_p(results$bm_ps_plots)

l_m <- rbind(c(1, 2), c(3, 4))

c(p2, bm_p2) %<-% map(list(p2, bm_p2), function(p) p + labs(y = ""))

bm_p1 <- 
  bm_p1 + 
  theme(legend.position = "none") + 
  labs(x = "Propensity Score", y = "SBM")
p2    <- p2    + labs(x = "")
p1    <- 
  p1 + 
  theme(legend.position = c(0.7, 0.9)) + 
  labs(y = "Overall")
# p2 <- 
#   results$overall_ps_plots$matched +
#   labs(x = "", y = "") + 
#   scale_fill_manual(labels = c("BEV-", "BEV+"), values = c("grey10", "grey60")) + 
#   theme(
#     axis.text.x = element_blank(), 
#     axis.ticks.x = element_blank(),
#     legend.position = c(0.8, 0.7), 
#     legend.background = element_blank()
#     )

png("figs/ps.png", units = "in", width = 4, height = 4, res = 300)
grid.arrange(p1, p2, bm_p1, bm_p2, layout_matrix = l_m)
dev.off()
grid.arrange(p1, p2, bm_p1, bm_p2, layout_matrix = l_m)
```


## Standardized mean differences


```{r}

library(ggsci)

smd_plot <- 
  results$tom %>% 
    imap_dfr(function(tb, nm) {
      nm <- gsub("_data$", "", nm)
      data.frame(
        mdl = nm,
        vr  = rownames(tb),
        smd = tb[,5],
        stringsAsFactors = FALSE
      )
    }) %>% 
    separate("mdl", into = c("match", "pop"), "_", fill = "right") %>%
    modify_at("pop", function(a) ifelse(is.na(a), "Overall", "SBM")) %>% 
    rename(term = vr) %>% 
    modify_at("smd", ~ as.numeric(gsub("<", "", .x))) %>%
    fix_term_names() %>% 
    filter(!is.na(smd)) %>% 
    filter(!grepl("bmab", tolower(term))) %>% 
    modify_at("term", ~ trimws(gsub("\\(%\\)|:", "", .x))) %>% 
    modify_at("term", 
      ~ str_replace_all(.x, 
        c("n_carbopl.*" = "Carboplatin",
          "n_pemetrexe.*" = "Pemetrexed",
          "n_dexameth.*" = "Dexamethasone",
          "n_paclitax.*" = "Paclitaxel",
          "n_cisplat.*" = "Cisplatin",
          "B_Metro" = "Metro",
          "race.*" = "Nonwhite",
          " = " = "",
          "= " = "",
          "histo.*" = "Adenocarcinoma",
          "^age$" = "Age"
          )
        )
    ) %>% 
    modify_at("match", str_to_title) %>% 
    filter(!(grepl("Stage", term) & pop == "SBM")) %>% 
    ggplot(aes(x = smd, y = reorder(term, smd), color = match)) + 
    geom_point() + 
    facet_wrap("pop") + 
    #scale_color_jco() + 
    scale_color_grey() + 
    #scale_shape_manual(values = c(1, 16)) + 
    theme_bw() + 
    theme(
      plot.title = element_text(face = "bold", size = rel(1.2), hjust = 0.5),
      text = element_text(),
      axis.title = element_text(face = "bold",size = rel(1)),
      axis.title.y = element_text(color = "black", angle = 90, vjust = 2),
      axis.title.x = element_text(vjust = -0.2),
      axis.text = element_text(), 
      axis.line = element_line(colour = "black"),
      axis.ticks = element_line(),
      panel.grid.major = element_line(colour = "#f0f0f0"),
      panel.grid.minor = element_blank(),
      legend.key = element_rect(colour = NA),
      legend.position = "bottom",
      legend.direction = "horizontal",
      legend.key.size = unit(0.2, "cm"),
      legend.title = element_text(face = "italic"),
      plot.margin = unit(c(10,5,5,5), "mm"),
      strip.background = element_rect(colour = "#f0f0f0", fill = "#f0f0f0"),
      strip.text = element_text(face = "bold")
    ) + 
    labs(x = "Standardized Mean Difference", y = "", color = "")

png("figs/smd-plot.png", units = "in", width = 6, height = 4, res = 300)
smd_plot
dev.off()
smd_plot
```



















